Extrinsic Type Inference (DRAFT 2025-06-08)

### 2025-07-09 extrinsic_type_inference_paper/paper.tex
add generator examples

\TODO{discuss recursive types}

\TODO{discuss regular trees}

>>>>

\TODO{discuss implicit and flow based approaches}

\TODO{discuss universal, existential, iso-recursive types}

\TODO{note how our structural requirements on recursive types prevent typing generators}

\TODO{mention regular tree reasoning}

\TODO{discuss how every types of expresions are implictly determine}

\TODO{discuss how types are iso-recursive, but are implicitl}
